NMRlipids III: Lipid-cholesterol interactions in atomistic resolution molecular dynamics simulations

### 2020-06-01 MANUSCRIPT/manuscript.tex
Update manuscript
Update manuscript.tex

@@

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
% Put your acknowledgments here.
\end{acknowledgments}

>>>>

\author{Jesper J. Madsen}
\affiliation{Department of Global Health, College of Public Health}
\affiliation{University of South Florida}

@@

     Lipid14\cite{walker15}     & POPC   & 120 & 8 & 6\% &  3968 & 303 & 200 & 200 & [\citenum{lipid14sys1}]$^*$ & SI \\ 
                          & POPC   & 108  & 20  & 16\% & 3968  & 303  & 200 & 200 & [\citenum{lipid14sys2}]$^*$ & SI    \\
                          & POPC   &  84  & 44 &  34\% & 3968  & 303  & 200 & 200 & [\citenum{lipid14sys3}]$^*$ & SI    \\
                             & POPC   & 64  & 64 & 50\% & 3968  & 303  & 200 & 200 & [\citenum{lipid14sys4}]$^*$ & SI    \\
                             & POPC   &  52  & 76 & 59\% & 3968  & 303  & 200 & 200 & [\citenum{lipid14sys5}]$^*$ & SI    \\

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
JJM thanks the Amber community (Benjamin Madej from the Walker lab and Callum Dickson from the Gould lab) for technical assistance related to the lipid14 force field parameters.
\end{acknowledgments}
